Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2017-03-10 Draft_1.tex
Added section regarding sanity checks using noun-verb relationship knowledge

\subsubsection{Context}
\label{sec:DisambiguationContext}
The context required for disambiguation exists in the STS. Two algorithms for disambiguation using this context have been implemented, one using hyponyms and one using hypernyms.

@@

>>>>

\subsubsection{Context}
\label{sec:DisambiguationContext}
The context used for disambiguation its taken from two sources, the STS and knowledge of noun-verb relationships (the latter is discussed in the \hyperref[Sanity]{Sanity Checking Section}).

Initially, the context contained in the STS is used. Two algorithms for disambiguation using this context have been implemented, one using hyponyms and one using hypernyms.

@@

\subsubsection{Sanity Checking}
\label{Sanity}
Given the sentence:
\[He\: fixed\: the\: bug\]
The reader knows that "bug" refers to a computer bug, due to its use with the verb "fixed". So far, the system has no way of modelling the contextual effects of nouns on verbs, so the system is likely to produce invalid sentences. For this reason, post-disambiguation sanity checks occur.

Though a proposed feature, WordNet does not currently contain relationships between nouns and verbs \cite{WN4Verbs}. For this reason, the information had to be extracted from the available corpus. It was decided that half of the test corpus would be used for the extraction, so that test data used for evaluation would be completely new to the system.

Listing \ref{lst:verbDistance} shows the algorithm used for extracting this information. Nouns which occur in the same sentence as a specific Verb are considered valid partners to the Verb, and are added to a dictionary for quick lookup.

\begin{lstlisting}[numbers=left, numberstyle=\small, caption={The noun-verb relationship learning algorithm}, captionpos=b, label={lst:verbDistance}]
FUNCTION verbDistance(verb, sentence):
	FOR word in sentence LOOP
		IF word is a noun THEN
			outputList.append(word.synset)
		END IF
	END LOOP
	RETURN outputList
END FUNCTION

FOR sentence in inputCorpus LOOP
	FOR every verb in sentence LOOP
		update contents of verbDict[verb.synset] 
		to include verbDistance(verb, sentence)
	END LOOP
END LOOP
\end{lstlisting}

Initially, the sentence is disambiguated, using the method described \hyperref[sec:ImplementedDisambiguation]{previously}. The outputted sentence is then checked for correctness by the function sanityCheck, as shown in Listing \ref{lst:sanityCheck}. If a synset is found to be incompatible with others in the sentence, it is added to a blacklist, and its corresponding word is disambiguated again, ignoring the previous meaning.

\begin{lstlisting}[numbers=left, numberstyle=\small, caption={The sanityCheck function}, captionpos=b, label={lst:sanityCheck}]
FUNCTION sanityCheck(inputSentence, nounDict, verbDict):
    sane = False
    FOR word in inputSentence LOOP
        IF word is a noun THEN
            nounList.append(word)
        ELSE IF word is a verb THEN
            verbList.append(word)
        END IF
    END LOOP
    WHILE not sane LOOP
        sane = True
        FOR verb in verbList LOOP
            IF verb in verbDict THEN
                plausibleNouns =  verbDict[verb]
                IF nounList and plausibleNouns share common words THEN
                    verbList.remove(verb)
                ELSE
                    blackList.append(verb)
                    verbList.remove(verb)
                    Run disambiguation again with blacklist
                END IF
            END  IF
		END LOOP
	END LOOP
END FUNCTION
\end{lstlisting}

It may be noted that sanityCheck only considers verb incorrectness. As stated in the \hyperref[Verbs]{WordNet section}, for each word, there is likely to be a larger set of synsets when compared to nouns. With this knowledge, we can assume that the likelyhood of an incorrect result for a verb is higher than that of a noun.
